---
title: "Predicting Correct Equipment Use"
author: "Andew Elliott"
date: "Wednesday, October 21, 2015"
output:
  html_document:
    keep_md: yes
---
Prepare data, including splitting the "pml-training.csv" into training and testing sets.  The "pml-testing.csv"" set gets held out for a very final test, as finalTestSet

```{r, echo=FALSE}
options(width=200)
require(randomforest)
require(caret)
trainingSet<-read.csv("../pml/pml-training.csv")
finalTestSet<-read.csv("../pml/pml-testing.csv")
training<-read.csv("../pml/pml-training.csv")
test<-read.csv("../pml/pml-testing.csv")
#pml<-pml1[sample(nrow(pml1), 4000),]

#inTrain <- createDataPartition(y=pml$classe, p=0.75, list=FALSE)
#trainSet <- pml[inTrain,]
#testSet <- pml[-inTrain,]


#require(rattle)
#require(rpart.plot)
#source("learnRepeatVisits.R")
#makeBehaviourData("3220")
#makeDeviceData("2000")
```

Exclude Contextual columns which would use order or time to predict outcome
```{r}
trainingSet<-trainingSet[,-1:-6]
#testSet<-testSet[,-1:-6]
finalTestSet<-finalTestSet[,-1:-6]
print(dim(trainingSet))

training<-training[,7:160]
test<-test[,7:160]
print(dim(training))

```

Exclude Near Zero Variability and those with predominantly NA columns
```{r}
dim(trainingSet)
nzv <- nearZeroVar(trainingSet, freqCut=10/1)
trainingSet <- trainingSet[,-nzv]
finalTestSet <- finalTestSet[,-nzv]
dim(trainingSet)
predomNA<-apply(is.na(trainingSet),2,mean)>0.9
trainingSet <-trainingSet[,-predomNA]
finalTestSet <-finalTestSet[,-predomNA]
dim(trainingSet)

mostly_data<-apply(!is.na(training),2,sum)>19621
training<-training[,mostly_data]
test<-test[,mostly_data]
dim(training)


```

Subset a training set (small for time considerations)
```{r}
inTrain <- createDataPartition(y=trainingSet$classe, p=0.05, list=FALSE)
trainSet <- trainingSet[inTrain,]
testSet <- trainingSet[-inTrain,]
print(dim(trainSet))

InTrain<-createDataPartition(y=training$classe,p=0.03,list=FALSE)
training1<-training[InTrain,]
print(dim(training1))


```


Fit a Random Forest model
```{r}
#fitControl <- trainControl(method = "cv", number = 5)
#modFit<- train(classe ~ . , method="rf", data=trainSet, trControl=fitControl, prox=TRUE, allowParallel=TRUE)
#modFit

rf_model<-train(classe~.,data=training1,method="rf",
                trControl=trainControl(method="cv",number=5),
                prox=TRUE,allowParallel=TRUE)
print(rf_model)


```
Final Model
```{r}
modFit$finalModel
#predictions<-predict(modFit, newdata=finalTestSet)
#length(predictions)
#length(finalTestSet$classe)
#confusionMatrix(predictions, testing$classe)
```                
